
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingItem}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/nelson-matos-04191112a/}{\Large Nelson Matos}} & Email : \href{mailto:nmatos580@gmail.com}{nmatos580@gmail.com}\\
  \href{https://www.linkedin.com/in/nelson-matos-04191112a/}{Linkedin Profile} & Mobile : \href{tel:+15802159353}{(580) 215-9353} \\
  \href{https://github.com/matos-nelson}{Github Profile}
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}

  \begin{description}
    \setlength\itemsep{0em}
    \item[Languages:]{C, C++, .NET Framework, .NET Core, Python, Javascript, SQL, Java}
    \item[Cloud Technologies:]{Amazon Web Services (AWS), Microsoft Azure}
    \item[Javascript Frameworks:]{Angular, React}
  \end{description}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Connect For Health Colorado (C4)}{Denver, CO (Remote)}
      {Full Stack Software Developer}{Sep. 2021 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Experience with designing and building continuous deployment/ continuous integration pipelines using Jenkins and utilizing Docker containers for deployment.}
        \resumeItem{}
          {Experience with integrating message queue products such as RabbitMQ and Kafka for communication between microservices and external applications.}
        \resumeItem{}
          {Build scalable and responsive Web API’s and Web services with a micro-service architecture, using Java SpringBoot/WebFlux, to make software highly testable using unit and integration testing methods.}
        \resumeItem{}
          {Responsible for architecting software systems that are fault tolerant, available and scalable with cloud infrastructure utilizing Amazon Web Services.}
        \resumeItem{}
          {Practiced test driven development techniques when implementing requirements to provide reliable and working software using unit/integration testing libraries such as Junit, Mockito and WireMock.}
        \resumeItem{}
          {Created a test wrapper that can be used in development/production environments that keeps track of code coverage during real user interaction.}
        \resumeItem{}
          {Work closely with product owner in backlog management and continuous delivery of new features and enhancements.}
        \resumeItem{}
          {Experience with Agile software development and Atlassian tools(JIRA, Confluence, BitBucket, Bamboo, Fisheye).}
        \resumeItem{}
          {Experience with mentoring Junior developers during the onboarding process and facilitate growth during development stages.}
        \resumeItem{}
          {Experience with building front end application utilizing Angular and React javascript frameworks.}
        \resumeItem{}
          {Experience with designing, creating and maintaining PostgreSQL databases.}
      \resumeItemListEnd

    \resumeSubheading
      {Northrop Grumman}{Oklahoma City, OK}
      {Scrum Master / Software Engineer III}{Nov. 2017 - Sep. 2021}
      \resumeItemListStart
        \resumeItem{}
          {Used Green Hills Integrity, VxWorks to develop RTOS for embedded systems.}
        \resumeItem{}
          {Modernized legacy embedded systems in order for source to be testable and compatible with a simulated environment by creating an abstract layer.}
        \resumeItem{}
          {Designed and developed an automated testing framework to work with various embedded systems that provided unit and integration testing capabilities.}
        \resumeItem{}
          {Experience with designing and building continuous deployment/ continuous integration pipelines using Atlassian Bamboo utilizing Docker and Karaf containers for deployment.}
        \resumeItem{}
          {Build scalable and responsive Web API's and Web services with a micro-service architecture, using Java SpringBoot/WebFlux, to make software highly testable using unit and integration testing methods.}
        \resumeItem{}
          {Practiced test driven development techniques when implementing requirements to provide reliable and working software using unit/integration testing libraries such as Junit, Mockito and WireMock.}
        \resumeItem{}
          {Experience with designing and maintaining standard RDBMS databases (MySQL, Oracle, PostgreSQL).}
        \resumeItem{}
          {Managed and deployed source code repositories using source control tools such as GIT.}
        \resumeItem{}
          {Experience with Agile software development and Atlassian tools(JIRA, Confluence, BitBucket, Bamboo, Fisheye).}
      \resumeItemListEnd

    \resumeSubheading
      {Configurely LLC}{Oklahoma}
      {Founder/Project Manager}{Jul. 2017 - Aug. 2020}
      \resumeItemListStart
        \resumeItem{}
          {Executed hands on Research, Development, and Planning (RDP) to create a detailed front-end design, technical design, and implementation plan for developing custom software for clients.}
        \resumeItem{}
          {Consult with client(s) to identify key requirements, defined project scope, developed project plan and schedule.}
        \resumeItem{}
          {Delegate and prioritize workflow to team members, troubleshoot and resolve technical issues, and diligently maintain company’s response tracking database. }
        \resumeItem{}
          {Provided leadership to internal teams on projects and responsible for ensuring teams met all milestones and goals as laid out in project plans.}
        \resumeItem{}
          {Compile detailed descriptions of user needs, program functions and steps required to develop or modify software.}
        \resumeItem{}
          {Build and maintain high volume database structures using Entity Framework for SQL server and PostgreSQL databases.}
        \resumeItem{}
          {Managed and deployed source code repositories using source control tools such as GIT and TFS.}
        \resumeItem{}
          {Build scalable, responsive and highly available Web API's and Web services with a clean architecture, using .NET Core framework, to make software highly testable using unit and integration testing methods.}
        \resumeItem{}
          {Documented Web API's and Web services using Swagger UI and Open API.}
        \resumeItem{}
          {Designed and developed front end user interfaces using Bootstrap and React javascript framework.}
        \resumeItem{}
          {Created and provided code coverage documentation that showed the effectiveness of developed Web API's and front end user interfaces.}
        \resumeItem{}
          {Created detailed development operation pipelines to provide Continuous Integration and Continuous Deployment by using services such as Jenkins and TFS.}
      \resumeItemListEnd

    \resumeSubheading
      {CACI International INC}{Lawton, OK}
      {Software Engineer I/II}{Aug. 2015 - Oct. 2017}
      \resumeItemListStart
        \resumeItem{}
          {Organized the transition of AFATDS software by developing an AFATDS build environment and establishing an AFATDS development environment.}
        \resumeItem{}
          {Upgrade AFATDS to allow installation on Windows 10 by updating external software.}
        \resumeItem{}
          {Implemented new ATACMS HE Rocket Munition into AFATDS Java UI and ADA services.}
        \resumeItem{}
          {Upgraded AFATDS MIDB Java interface to allow large MIDB data polls.}
        \resumeItem{}
          {Implement functionality for AFATDS to designate multiple Airspace Coordinating Agencies to allow airspace coordination during mission processing.}
        \resumeItem{}
          {Developed a tool in Java to determine what ADA executables were affected based on ADA file changes by reversing the ADA compilation process.}
        \resumeItem{}
          {Developed an ADA/Java tool that performed unit tests on receiving and transmit of 6017C VMF Messages.}
        \resumeItem{}
          {Analyzed software requirements to determine feasibility of design within time and cost constraints.}
        \resumeItem{}
          {Identified creative solutions to improve system and product offerings. Represented the organization in providing solutions to difficult technical problems.}
        \resumeItem{}
          {Provided functional and empirical analysis related to the design, development, and implementation of software systems, including, but not limited to application software, utility software, development software, and diagnostic software.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science;  GPA: 3.9}{Aug. 2020 -- Aug. 2022}
    \resumeSubheading
      {Cameron University}{Lawton, Oklahoma}
      {Bachelor of Science in Computer Science;  GPA: 3.78}{Aug. 2009 -- Dec. 2015}
  \resumeSubHeadingListEnd

%-----------Certification-----------------
\section{Certification}
  \resumeSubHeadingListStart
  \resumeSubheadingItem
  {AWS Cloud Practioner}{Dec. 2022}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}